---
title: "jeksterslabRlinreg"
author: "Ivan Jacob Agaloos Pesigan"
date: "`r Sys.Date()`"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/jeksterslabds/jeksterslabRlinreg.svg?branch=master)](https://travis-ci.com/jeksterslabds/jeksterslabRlinreg)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/jeksterslabds/jeksterslabRlinreg?branch=master&svg=true)](https://ci.appveyor.com/project/jeksterslabds/jeksterslabRlinreg)
[![codecov](https://codecov.io/github/jeksterslabds/jeksterslabRlinreg/branch/master/graphs/badge.svg)](https://codecov.io/github/jeksterslabds/jeksterslabRlinreg) 
<!-- badges: end -->

`jeksterslabRlinreg` is a collection of functions that I find useful in studying linear regression concepts and methods.

## Installation

You can install the released version of `jeksterslabRlinreg` from [GitHub](https://github.com/jeksterslabds/jeksterslabRlinreg) with:

```r
library(devtools)
install_github("jeksterslabds/jeksterslabRlinreg")
```

## Example

```{r, parameters, echo = FALSE}
n <- 100
sigma2 <- runif(
  n = 1,
  min = 9,
  max = 15
)
beta <- runif(
  n = sample(
    x = 2:5,
    size = 1
  ),
  min = 1,
  max = 3
)
```

```{r, generate_data, echo = FALSE}
X <- matrix(
  data = NA,
  nrow = n,
  ncol = length(beta)
)
for (i in 1:length(beta)) {
  if (i == 1) {
    X[, i] <- rep(
      x = 1,
      times = n
    )
  } else {
    X[, i] <- runif(
      n = n,
      min = -5,
      max = 5
    )
  }
}
y <- X %*% beta + rnorm(
  n = n,
  sd = sqrt(sigma2)
)
```

The main function in this package is `linreg()`.
It fits a linear regression model using ordinary least squares.
The required arguments include:

  - **X**: The data matrix
    \eqn{\mathbf{X}}
    is an \eqn{n \times k} matrix
    of \eqn{n} observations
    of \eqn{k} regressors,
    which includes a regressor
    whose value is 1 for each observation.
  - **y**: The vector
    \eqn{\mathbf{y}}
    is an \eqn{n \times 1} vector
    of observations on the regressand variable.

```{r, example}
library(jeksterslabRlinreg)
linreg(
  X = X,
  y = y,
  FUN = betahat_inv,
  output = c("coef", "ci", "model", "anova")
)
```

See [GitHub Pages](https://jeksterslabds.github.io/jeksterslabRlinreg/index.html)
for package documentation.
