---
title: "jeksterslabRlinreg"
author: "Ivan Jacob Agaloos Pesigan"
date: "`r Sys.Date()`"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/jeksterslabds/jeksterslabRlinreg.svg?branch=master)](https://travis-ci.com/jeksterslabds/jeksterslabRlinreg)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/jeksterslabds/jeksterslabRlinreg?branch=master&svg=true)](https://ci.appveyor.com/project/jeksterslabds/jeksterslabRlinreg)
[![codecov](https://codecov.io/github/jeksterslabds/jeksterslabRlinreg/branch/master/graphs/badge.svg)](https://codecov.io/github/jeksterslabds/jeksterslabRlinreg) 
<!-- badges: end -->

`jeksterslabRlinreg` is a collection of functions that I find useful in studying linear regression concepts and methods.

## Installation

You can install the released version of `jeksterslabRlinreg` from [GitHub](https://github.com/jeksterslabds/jeksterslabRlinreg) with:

```r
library(devtools)
install_github("jeksterslabds/jeksterslabRlinreg")
```

## Example

### Data

In this example, we examine the association between `GPA` and `LSAT` scores.

See `jeksterslabRdatarepo::law()` for more information about the data set used.

```{r, echo = FALSE}
LSAT <- jeksterslabRdatarepo::law$LSAT
GPA <- jeksterslabRdatarepo::law$GPA
X <- cbind(
  Intercept = 1,
  GPA = GPA
)
y <- matrix(
  data = LSAT,
  ncol = 1
)
colnames(y) <- "LSAT"
head(X)
head(y)
```

### `jeksterslabRlinreg::linreg()`

The `jeksterslabRlinreg::linreg()` function
fits a linear regression model using `X` and `y`.
In this example, `X` consists of a column of constants and `GPA`
and `y` consists of `LSAT` scores.

The output includes the following:

- ANOVA table
- Table of regression coefficients with the following columns
  - Regression coefficients
  - Standard errors
  - $t$ statistic
  - $p$ value
  - Standardized coefficients
- Confidence intervals (0.05, 0.5, 2.5, 97.5, 99.5, 99.95)
- Means and standard deviations
- Scatterplot matrix
- Residual plots

```{r}
jeksterslabRlinreg::linreg(
  X = X,
  y = y
)
```

See [GitHub Pages](https://jeksterslabds.github.io/jeksterslabRlinreg/index.html)
for package documentation.
