---
title: "Introduction to jeksterslabRlinreg"
author: "Ivan Jacob Agaloos Pesigan"
date: "`r Sys.Date()`"
description: >
  Learn how to get started with the basics of jeksterslabRlinreg.
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Introduction to jeksterslabRlinreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 5,
  fig.height = 5,
  out.width = "100%"
)
```

`jeksterslabRlinreg` is a collection of functions that I find useful in studying linear regression concepts and methods.

## Installation

You can install the released version of `jeksterslabRlinreg` from [GitHub](https://github.com/jeksterslabds/jeksterslabRlinreg) with:

```r
library(devtools)
install_github("jeksterslabds/jeksterslabRlinreg")
```

## Example

### Data

In this hypothetical example,
we are interested in the association between wages and education.
The regressor variable is years of education.
The regressand variable is hourly wage in US dollars.

```{r, echo = FALSE}
wages <- jeksterslabRdatarepo::wages
x <- wages$education
y <- wages$wages
n <- length(x)
obj <- lm(y ~ x)
beta <- unname(coef(obj))
# covariance structure
beta1 <- beta[1]
beta2 <- beta[2]
sigma2x <- var(x)
sigma2y <- var(y)
# sigma^2 has some discrepancy
# sigma2epsilon <- summary(obj)$sigma^2
sigma2epsilon <- sigma2y - (beta2^2 * sigma2x)
# mean structure
mux <- mean(x)
```

```{r, echo = FALSE}
x <- as.integer(rnorm(n = n, mean = mux, sd = sqrt(sigma2x)))
epsilon <- rnorm(n = n, mean = 0, sd = sqrt(sigma2epsilon))
y <- beta1 + beta2 * x + epsilon
X <- cbind(
  constant = 1,
  education = x
)
y <- matrix(
  data = y,
  ncol = 1
)
colnames(y) <- "wages"
head(X)
head(y)
```

### `jeksterslabRlinreg::linreg()`

The `jeksterslabRlinreg::linreg()` function
fits a linear regression model using `X` and `y`.
In this example, `X` consists of a column of constants and years of `education`
and `y` consists of hourly `wages` in US dollars.

The output includes the following:

- Model assessment
- ANOVA table
- Table of regression coefficients with the following columns
  - Regression coefficients
  - Standard errors
  - $t$ statistic
  - $p$ value
  - Standardized coefficients
- Confidence intervals (0.05, 0.5, 2.5, 97.5, 99.5, 99.95)
- Means and standard deviations
- Scatterplot matrix
- Residual plots

```{r, eval = FALSE}
jeksterslabRlinreg::linreg(
  X = X,
  y = y
)
```
