---
title: "Introduction to jeksterslabRlinreg"
author: "Ivan Jacob Agaloos Pesigan"
date: "`r Sys.Date()`"
description: >
  Learn how to get started with the basics of jeksterslabRlinreg.
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Introduction to jeksterslabRlinreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 5,
  fig.height = 5,
  out.width = "100%"
)
```

`jeksterslabRlinreg` is a collection of functions that I find useful in studying linear regression concepts and methods.

## Installation

You can install the released version of `jeksterslabRlinreg` from [GitHub](https://github.com/jeksterslabds/jeksterslabRlinreg) with:

```r
library(devtools)
install_github("jeksterslabds/jeksterslabRlinreg")
```

## Example

### Data

In this example, we examine the association between `GPA` and `LSAT` scores.

See `jeksterslabRdatarepo::law()` for more information about the data set used.

```{r, echo = FALSE}
LSAT <- jeksterslabRdatarepo::law$LSAT
GPA <- jeksterslabRdatarepo::law$GPA
X <- cbind(
  Intercept = 1,
  GPA = GPA
)
y <- matrix(
  data = LSAT,
  ncol = 1
)
colnames(y) <- "LSAT"
head(X)
head(y)
```

### `jeksterslabRlinreg::linreg()`

The `jeksterslabRlinreg::linreg()` function
fits a linear regression model using `X` and `y`.
In this example, `X` consists of a column of constants and `GPA`
and `y` consists of `LSAT` scores.

The output includes the following:

- ANOVA table
- Table of regression coefficients with the following columns
  - Regression coefficients
  - Standard errors
  - $t$ statistic
  - $p$ value
  - Standardized coefficients
- Confidence intervals (0.05, 0.5, 2.5, 97.5, 99.5, 99.95)
- Means and standard deviations
- Scatterplot matrix
- Residual plots

```{r}
jeksterslabRlinreg::linreg(
  X = X,
  y = y
)
```
